Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-07-28 bbbq_article.tex
EOD

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolutionary conservation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{transitions.png}
  \caption{
    Transitions in TMHs that occur more often then expected by chance,
    for a confidence interval of 5 percent.
    Table \ref{tab:transitions} shows the transition counts.
    \richel{
      stub figure
    }
  }
  \label{fig:transitions}
\end{figure}

\begin{table}[!htbp]
  \input{table_transitions.latex}
  \caption{
    Transitions counts, where the row indicates the source state,
    and the column indicates the target state.
    First number per cell is the observed number of this state transition,
    where the second number is the expected number of this state transition
    as predicted by chance.
    An asterisk behind the observed count indicates that this count
    is unlikely to be caused by chance only.
    Figure \ref{fig:transitions} shows which transition counts are 
    unlikely to be caused by chance only.
  }
  \label{tab:transitions}
\end{table}

@@

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Differences with Bianchi et al., 2017}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A part of this study does the same analysis as Bianchi et al., 2017.
Here we describe the deviations, which are about the use of different
software and the use of a different definition of what a binder is.

\paragraph{TMH prediction software}

The earlier study uses TMHMM, which has a restricted software license.
Instead, we chose to use PureseqTM, which is free and open source.

\paragraph{IC50 prediction software}

The earlier study uses a hand-crafted method, that only works on MHC-I.
Instead, we use MHCnuggets, which (1) free and open source, and (2) predicts
IC50s on both MHC-I and MHC-II.

\paragraph{Definition of what a binder is}

The earlier study defines a peptide a binder (for a haplotype), 
if \emp{within the peptide} in which it is found, 
is within the peptides with the 2\% lowest IC50 values.
This can be seen at \url{https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/master/predict-binders.R},
where the binders are written to file.

In this study, a peptide is defined a binder (for a haplotype), 
if \emp{within a proteome} in which it is found, 
is within the peptides with the 2\% lowest IC50 values.
